---
title: "Data Processing in R"
author: "Nader Tavana"
output:
  html_document: default
  pdf_document: default
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### read data 
```{r}
Badges<-read.csv("Badges.csv.gz")
Comments<-read.csv("Comments.csv.gz")
PostLinks<-read.csv("PostLinks.csv.gz")
Posts<-read.csv("Posts.csv.gz")
Tags<-read.csv("Tags.csv.gz")
Users<-read.csv("Users.csv.gz")
Votes<-read.csv("Votes.csv.gz")

```

### load packages
```{r echo = T,error=FALSE,warning=FALSE,message=FALSE,results = 'hide'}
library(sqldf)
library(dplyr)
library(data.table)
library(microbenchmark)
```

## 1)

#### 1)sql solution
```{r}
#sql solution

sqldf_solution1<-function(){sqldf("SELECT Posts.Title, RelatedTab.NumLinks
FROM
(SELECT RelatedPostId AS PostId, COUNT(*) AS NumLinks
FROM PostLinks
GROUP BY RelatedPostId) AS RelatedTab
JOIN Posts ON RelatedTab.PostId=Posts.Id
WHERE Posts.PostTypeId=1
ORDER BY NumLinks DESC")}


```
#### Intuitive interpretation:
We want to get the titles of questions ordered from the most linked one to the least linked one. We also want to see the number of times each question was linked.

\

#### 1)base functions
```{r}
#base functions
base_functions_solution1<-function(){

RelatedTab<-aggregate(PostLinks$RelatedPostId,by=list(PostLinks$RelatedPostId),FUN=length)

colnames(RelatedTab)<-c("PostId","NumLinks")

h<-merge(RelatedTab,Posts[Posts$PostTypeId==1,],by.x = "PostId",by.y = "Id")

v<-h[,c("Title","NumLinks")]

v<-v[order(-v$NumLinks),]}

#comparing
dplyr::all_equal(sqldf_solution1(),base_functions_solution1())


```
\

#### 1)dplyr solution
```{r}
#dplyr solution
dplyr_solutions1<-function(){RelatedTab2<-(PostLinks %>% count(RelatedPostId,name = "NumLinks") %>% rename(PostId=RelatedPostId))

Post_RelatedTab<-inner_join(Posts,RelatedTab2,by=c("Id"="PostId"))

Post_RelatedTab<-filter(Post_RelatedTab,PostTypeId==1)

Title_NumLinks<-select(Post_RelatedTab,Title,NumLinks) 

Title_NumLinks<-arrange(Title_NumLinks,desc(NumLinks))}

#comparing
dplyr::all_equal(sqldf_solution1(),dplyr_solutions1())


```
\

#### 1)data.table solution
```{r}

setDT(PostLinks)
setDT(Posts)

datatable_solution1<-function(){

RelatedTab3<-PostLinks[,.N,by=.(RelatedPostId)]

setnames(RelatedTab3,c("N","RelatedPostId"),c("NumLinks","PostId"))

Post_RelatedTab2<-merge.data.table(Posts,RelatedTab3,by.x="Id",by.y = "PostId")

Post_RelatedTab2<-Post_RelatedTab2[PostTypeId==1]

Title_NumLinks2<-Post_RelatedTab2[,.(Title,NumLinks)]

Title_NumLinks2<-setorder(Title_NumLinks2,-NumLinks)}

setDF(datatable_solution1())

#comparing
dplyr::all_equal(sqldf_solution1(),datatable_solution1())

```
\

#### 1)compare the execution times
```{r}
library(microbenchmark)
microbenchmark::microbenchmark(
    sqldf1=sqldf_solution1,
    base1=base_functions_solution1,
    dplyr1=dplyr_solutions1,
    data.table1=datatable_solution1
)
```


## 2)

#### 2)sql solution
```{r}
#sql solution

sqldf_solution2<-function(){sqldf("SELECT
      Users.DisplayName,
      Users.Age,
      Users.Location,
      SUM(Posts.FavoriteCount) AS FavoriteTotal,
      Posts.Title AS MostFavoriteQuestion,
      MAX(Posts.FavoriteCount) AS MostFavoriteQuestionLikes
FROM 
Posts JOIN Users ON Users.Id=Posts.OwnerUserId
WHERE Posts.PostTypeId=1
GROUP BY OwnerUserId
ORDER BY FavoriteTotal DESC
LIMIT 10")}


```
#### Intuitive interpretation:
We want to find ten users whose questions were liked the most in total. For each user we also want to know his age, location, the title of question which was liked the most among the ones asked by him, and the number of likes for this question

\

#### 2)base functions
```{r}
#base functions
base_functions_solution2<-function(){

join <- merge(Posts[Posts$PostTypeId == 1, ], Users, by.x = 'OwnerUserId', by.y = 'Id', all.x = T, all.y = F)
  aggregated <- do.call(data.frame, 
                    aggregate(
                      FavoriteCount ~ OwnerUserId,
                      data=join,
                      FUN=function(x) c(total = sum(x), max = max(x))))
  answer <- merge(aggregated, join, by.x = c('OwnerUserId', 'FavoriteCount.max'), 
                  by.y = c('OwnerUserId', 'FavoriteCount'), all.x = T, all.y = F)
  answer <- answer[c('DisplayName', 'Age', 'Location', 'FavoriteCount.total', 'Title', 'FavoriteCount.max')]
  answer <- answer[order(answer$FavoriteCount.total, decreasing = T), ]
  colnames(answer)[c(4, 5, 6)] = c('FavoriteTotal', 'MostFavoriteQuestion', 'MostFavoriteQuestionLikes')
  rownames(answer) = NULL
  head(answer, 10)}

#comparing
dplyr::all_equal(sqldf_solution2(),base_functions_solution2())


```
\

#### 2)dplyr solution
```{r}
#dplyr solution
dplyr_solutions2<-function(){
    left_join(filter(Posts, PostTypeId == 1 & !is.na(OwnerUserId) & !is.na(FavoriteCount)), Users, 
          c('OwnerUserId' = 'Id')) %>%
  group_by(OwnerUserId) %>%
  select(DisplayName, Age, Location, FavoriteCount, Title, OwnerUserId) %>%
  summarise(
    DisplayName = first(DisplayName),
    Age = first(Age),
    Location = first(Location),
    MostFavoriteQuestion = Title[which.max(FavoriteCount)],
    FavoriteTotal = sum(FavoriteCount),
    MostFavoriteQuestionLikes = max(FavoriteCount)) %>%
  select(DisplayName:MostFavoriteQuestionLikes) %>%
  arrange(desc(FavoriteTotal)) %>%
  head(10) -> a2_dplyr}

#comparing
dplyr::all_equal(sqldf_solution2(),dplyr_solutions2())


```
\

#### 2)data.table solution
```{r}


PostsDT=setDT(Posts)

datatable_solution2<-function(){

  join <- merge(PostsDT[PostTypeId == 1], Users, by.x = 'OwnerUserId', by.y = 'Id', all.x = T, all.y = F)
  join <- na.omit(join, cols = c('OwnerUserId', 'FavoriteCount'))
  aggregated <- join[, .(MFQ = sum(FavoriteCount), MFQL = max(FavoriteCount)), by = OwnerUserId][order(-MFQ)]
  answer <- merge(aggregated, join, by.x = c('OwnerUserId', 'MFQL'), 
                  by.y = c('OwnerUserId', 'FavoriteCount'), all.x = T, all.y = F)
  answer <- answer[, .(DisplayName, Age, Location, MFQ, Title, MFQL)][order(-MFQ)]
  colnames(answer)[c(4, 5, 6)] = c('FavoriteTotal', 'MostFavoriteQuestion', 'MostFavoriteQuestionLikes')
  head(answer, 10)}

setDF(datatable_solution2())

#comparing
dplyr::all_equal(sqldf_solution2(),datatable_solution2())

```
\

#### 2)compare the execution times
```{r}
library(microbenchmark)
microbenchmark::microbenchmark(
    sqldf2=sqldf_solution2,
    base2=base_functions_solution2,
    dplyr2=dplyr_solutions2,
    data.table2=datatable_solution2
)
```

# 3)

#### 3)sql solution
```{r}
#sql solution
sqldf_solution3<-function(){sqldf("SELECT
Posts.Title,
CmtTotScr.CommentsTotalScore
FROM (
SELECT
PostID,
UserID,
SUM(Score) AS CommentsTotalScore
FROM Comments
GROUP BY PostID, UserID
) AS CmtTotScr
JOIN Posts ON Posts.ID=CmtTotScr.PostID AND Posts.OwnerUserId=CmtTotScr.UserID
WHERE Posts.PostTypeId=1
ORDER BY CmtTotScr.CommentsTotalScore DESC
LIMIT 10
")}
```
#### Intuitive interpretation:
We want to find 10 questions under which author of the question got the biggest amount of score by making comments to this question. We want to see the titles of said questions and the sum of scores of comments made by the author of the question

\

#### 3)base functions
```{r}
#base functions
base_functions_solution3<-function(){CmtTotScr<-aggregate(Score~PostId+UserId,data=Comments,sum)

colnames(CmtTotScr)[3]<-"CommentsTotalScore"

CmtTotScr_Post<-merge(CmtTotScr,data.frame(Posts)[Posts$PostTypeId==1,],by.x =c("PostId","UserId") ,by.y = c("Id","OwnerUserId")) 

CmtTotScr_Post<-CmtTotScr_Post[order(-CmtTotScr_Post$CommentsTotalScore),]

v<-CmtTotScr_Post[,c("Title","CommentsTotalScore")]

v<-head(v,10)}

#comparing
dplyr::all_equal(base_functions_solution3(),sqldf_solution3())

```
\

#### 3)dplyr solution
```{r}
#dplyr solution
dplyr_solutions3=function(){CmtTotScr1<-Comments %>% group_by(PostId,UserId) %>% summarise(CommentsTotalScore=sum(Score))

CmtTotScr_Post2<-inner_join(CmtTotScr1,Posts,by=c("PostId"="Id","UserId"="OwnerUserId"))

CmtTotScr_Post2<-as.data.frame(filter(CmtTotScr_Post2,PostTypeId==1)) 

Title_CommentsTotalScore<-select(CmtTotScr_Post2,Title,CommentsTotalScore)

Title_CommentsTotalScore<-arrange(Title_CommentsTotalScore,desc(CommentsTotalScore))

Title_CommentsTotalScore<-top_n(Title_CommentsTotalScore,10)}

#comparing
dplyr::all_equal(dplyr_solutions3(),sqldf_solution3())

```
\

#### 3)data.table solution
```{r}
#data.table solution
setDT(Comments)
setDT(Posts)

datatable_solution3<-function(){n<-Comments[, .(CommentsTotalScore=sum(Score)),by=.(PostId,UserId)]

CmtTotScr_Post3<-merge.data.table(n,Posts,by.x =c("PostId","UserId") ,by.y = c("Id","OwnerUserId"))

CmtTotScr_Post3<-CmtTotScr_Post3[PostTypeId==1]

Title_CommentsTotalScore3<-CmtTotScr_Post3[,.(Title,CommentsTotalScore)][order(-
                                                                                CommentsTotalScore)][1:10,]}

setDF(datatable_solution3())

#comparing
dplyr::all_equal(datatable_solution3(),base_functions_solution3())

```
\

#### 3)compare the execution times

```{r}

library(microbenchmark)
microbenchmark::microbenchmark(
    sqldf3=sqldf_solution3,
    base3=base_functions_solution3,
    dplyr3=dplyr_solutions3,
    data.table3=datatable_solution3
)
```




# 4)

#### 4)sql solution
```{r}
sqldf_solution4<-function(){sqldf("SELECT DISTINCT
Users.Id,
Users.DisplayName,
Users.Reputation,
Users.Age,
Users.Location
FROM (
SELECT
Name, UserID
FROM Badges
WHERE Name IN (
SELECT
Name
FROM Badges
WHERE Class=1
GROUP BY Name
HAVING COUNT(*) BETWEEN 2 AND 10
)
AND Class=1
) AS ValuableBadges
JOIN Users ON ValuableBadges.UserId=Users.Id")}
```
#### Intuitive interpretation:
We want to find users which were assigned a class 1 badge, additionally the badge had to be assigned at least 2 times and at most 10 times. We want to see their ID, Display Name, Reputation, Age and Location.

\

#### 4)base functions
```{r}
#base functions
base_functions_solution4<-function(){e<-subset(Badges,Class==1,select=c(Name))

d<-aggregate(e$Name,by=list(e$Name),FUN=length)

colnames(d)<-c("Name","C")

d1<-subset(d,C>=2 & C<=10,select=c(Name))

b<-subset(Badges,Class==1,select = c(Name,UserId))

ValuableBadges<-subset(b,b$Name=='visas'|b$Name=='Sheriff'|b$Name=='Reversal'|b$Name=='Constable')

Users_ValueBadges<-merge(data.frame(Users) ,data.frame(ValuableBadges) ,by.x = "Id",by.y = "UserId")

v<-unique(Users_ValueBadges[c("Id","DisplayName","Reputation","Age","Location")]) }

#comparing
dplyr::all_equal(base_functions_solution4(),sqldf_solution4())

```
\

#### 4)dplyr solution
```{r}
#dolyr solution
dplyr_solutions4<-function(){t<-Badges %>% filter(Class==1) %>% count(Name)
t1<-t %>% filter(n>=2 & n<=10) %>% select(Name)

ValuableBadges2<-Badges %>% filter(Name %in% t1$Name,Class==1) %>% select(Name,UserId)

v<-inner_join(Users,ValuableBadges2,by=c("Id"="UserId"))

v<-distinct(v,Id,DisplayName,Reputation,Age,Location)}

#comparing
dplyr::all_equal(dplyr_solutions4(),sqldf_solution4())

```
\

#### 4)data.table solution
```{r}
#data.table solution
setDT(Badges)
setDT(Users)

datatable_solution4<-function(){t3<-Badges[Class==1,.N,by=.(Name)][N<=10 & N>=2][,.(Name)]

ValuableBadges3<-Badges[Name %in% c(t3[,Name])][Class==1]

Users_ValueBadges3<-merge.data.table(Users,ValuableBadges3,by.x="Id",by.y = "UserId")

Users_ValueBadges3<-unique(Users_ValueBadges3[,.(Id,DisplayName,Reputation,Age,Location)])}

setDF(datatable_solution4())

#comparing
dplyr::all_equal(datatable_solution4(),sqldf_solution4())

```
\

#### 4)compare the execution times
```{r}

microbenchmark::microbenchmark(
    sqldf4=sqldf_solution4,
    base4=base_functions_solution4,
    dplyr4=dplyr_solutions4,
    data.table4=datatable_solution4
)
```

\

# 5)

#### 5)sql solution
```{r}
#sql solution

sqldf_solution5<-function(){sqldf("SELECT
Questions.Id,
Questions.Title,
BestAnswers.MaxScore,
Posts.Score AS AcceptedScore,
BestAnswers.MaxScore-Posts.Score AS Difference
FROM (
SELECT Id, ParentId, MAX(Score) AS MaxScore
FROM Posts
WHERE PostTypeId==2
GROUP BY ParentId
) AS BestAnswers
JOIN (
SELECT * FROM Posts
WHERE PostTypeId==1
) AS Questions
ON Questions.Id=BestAnswers.ParentId
JOIN Posts ON Questions.AcceptedAnswerId=Posts.Id
WHERE Difference>50
ORDER BY Difference DESC
")}
```
#### Intuitive interpretation:
We want to find the questions where the difference = max - accepted is the highest and at least 50, where max - maximum score of an answer to question, accepted - score of the accepted answer.

In the output for each question we have to show its ID, title, max, accepted, difference [last three defined as above].

\

#### 5)base functions
```{r}
#base functions

base_functions_solution5<-function(){a<-Posts[Posts$PostTypeId == 2, c("Id", "ParentId", "Score")]

a1<-by(data=a,INDICES = list(a$ParentId),function(x) x[which.max(x$Score),])

BestAnswers<-do.call(rbind,a1)

colnames(BestAnswers)[3]<-"MaxScore"

Questions<-Posts[Posts$PostTypeId==1,]

Question_BestAnswer<-merge(Questions,BestAnswers,by.x="Id",by.y = "ParentId")

Question_BestAnswer[is.na(Question_BestAnswer)]<-0

Question_Post<-merge(Question_BestAnswer,Posts,by.x="AcceptedAnswerId",by.y = "Id")

names(Question_Post)[names(Question_Post)=="Score.y"]<-"AcceptedScore"

Question_Post[is.na(Question_Post)]<-0

Question_Post$Difference<-Question_Post$MaxScore - Question_Post$AcceptedScore

q<-Question_Post[Question_Post$Difference>50]

q<-q[order(-q$Difference)]

names(q)[names(q)=="Title.x"]<-"Title"

ans<-q[,c("Id","Title","MaxScore","AcceptedScore","Difference")]}

#comparing
dplyr::all_equal(sqldf_solution5(),base_functions_solution5())

```
\

#### 5)dplyr solution
```{r}
#dolyr solution
dplyr_solutions5<-function(){
    filter(Posts, PostTypeId == 2) %>%
  group_by(ParentId) %>%
  summarise(
    Id = ParentId[which.max(Score)],
    ParentId = ParentId[which.max(Score)],
    MaxScore = max(Score)) %>%
  right_join(filter(Posts, PostTypeId == 1), c('ParentId' = 'Id')) %>%
  left_join(Posts, c('AcceptedAnswerId' = 'Id')) %>%
  select(Id, Title = Title.x, MaxScore, AcceptedScore = Score.y) %>%
  mutate(Difference = MaxScore - AcceptedScore) %>%
  filter(Difference > 50 & !is.na(Difference)) %>%
  arrange(desc(Difference))}

#comparing
dplyr::all_equal(dplyr_solutions5(),sqldf_solution5())

```
\

#### 5)data.table solution
```{r}
#data.table solution
PostsDT=setDT(Posts)

datatable_solution5<-function(){
    BestAnswers <- PostsDT[PostsDT[PostTypeId == 2, .I[which.max(Score)], by = ParentId]$V1]
  BestAnswers <- BestAnswers[, .(Id, ParentId, MaxScore = Score)]
  Questions <- merge(PostsDT[PostTypeId == 1], BestAnswers, by.x = 'Id', by.y = 'ParentId', all.x = F, all.y = T)
  FinalJoin <- merge(Questions, PostsDT, by.x = 'AcceptedAnswerId', by.y = 'Id', all.x = T, all.y = F)
  answer <- FinalJoin[, .(Id, Title = Title.x, MaxScore, AcceptedScore = Score.y, 
                          Difference = MaxScore - Score.y)]
  answer[Difference > 50][order(-Difference)]}

setDF(datatable_solution5())

#comparing
dplyr::all_equal(datatable_solution5(),sqldf_solution5())

```
\

#### 5)compare the execution times
```{r}

microbenchmark::microbenchmark(
    sqldf5=sqldf_solution5,
    base5=base_functions_solution5,
    dplyr5=dplyr_solutions5,
    data.table5=datatable_solution5
)
```



### the End




